Diffantom: a software layer to build digital phantoms of whole-brain diffusion MRI

### 2015-07-15 paper/main.tex
fix fig02 and its caption #10

\begin{figure}[h!]
\begin{center}
\includegraphics[width=\linewidth]{figures/figure02}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:figure2} Figure \arabic{figure}. }%
{\textbf{A. Recommended use of \emph{diffantom}}.
The dataset can be used to test algorithms and pipelines against a perturbation that is
  introduced in \emph{diffantom}.
Perturbations can model typical artifacts found in \gls*{dmri} datasets or pathological conditions
  such as a tumor.
\textbf{B1. Tractogram of fibers crossing slice 56 of the \emph{diffantom}} represented over that corresponding
  slice of the \emph{b0} volume. \textbf{B2. Segmentation of some fiber bundles}: in blue color is represented
  the right \gls*{cst}, in red the left \gls*{cst}, and in green the forceps minor.
  The box includes the slice 56 of the \emph{b0} and the light gray shadow is the pial surface.
}
\end{figure}

>>>>

\begin{figure}[h!]
\begin{center}
\includegraphics[width=\linewidth]{figures/figure02}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:figure2} Figure \arabic{figure}. }%
{\textbf{A. Recommended use of \emph{diffantom}}.
The dataset can be used to test algorithms and pipelines against a perturbation that is
  introduced in \emph{diffantom}.
Perturbations can model typical artifacts found in \gls*{dmri} datasets or pathological conditions
  such as a tumor.
\textbf{B1. Tractogram of fibers crossing slice 56 of the \emph{diffantom}} represented over that corresponding
  slice of the \emph{b0} volume. \textbf{B2. Segmentation of some fiber bundles}: the right \gls*{cst} is
  represented in blue color, the left \gls*{cst} in red, and the forceps minor in green.
  The box includes the slice 56 of the \emph{b0} and the pial surface is represented with a light gray shadow.
}
\end{figure}
